---
name: Walter Quispe
position: "Data Scientist"
address: "Simón Bolívar E-1A, Bancopata, Cusco, Perú"
phone: +51 974 377 276
profilepic: wqv.png
www: walterqv.github.io/website/
email: "walter.quispe@upr.edu"
twitter: WalterqvPR
github: walterqv
linkedin: walterqv
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am aiming to deploy my professional knowledge in academia and industry to perform data-driven discovery and decision making process."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Experience

-   Apr 2023 - Present, **Full Time Adjunt Professor**
    -   Math and Stat Department. San Antonio Abad University, Cusco-Perú
        - Teaching Graduate and Undergraduate Courses: EP703AES Foundations of Probability, ME814AME Actuarial Statistics, ME841AME Multivariate Statistics I, ME842AME Didactics of Statistics.

 

-   Sep 2021 - Present, **Quantitative Risk Analyst**.
    -   Model Risk Management at First Bank of Puerto Rico.
        -   Understanding, Validating, and Developing advance Machine Learning and Statistical models to comply with regulatory requirements.

 

-   Sep 2020 - Sep 2021, **Data Scientist**.
    -   Artificial Intelligence at Banco Popular de Puerto Rico.
        -   Building intelligent systems by employing advanced Machine Learning algorithms in order to advance business strategy.

 

-   Jan 2020 - Sep 2020, **Data Science Post Doctoral Research**.
    -   University of Puerto Rico at Mayaguez.
        -   "Collaborative Research: Atomic Level Structural Dynamics in Catalysts." Harnessing tools from machine learning to perform data-driven discovery in catalysts, NSF Harnessing Data Revolution Program, Grant OAC-1940179, UPRM.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ph.D. Computing and Information Science", "2013-2019", "Univ. of Puerto Rico", "Mayaguez, Puerto Rico, USA",
  "M.Sc. Mathematics and Statistics", "2003-2006", "Univ. of Puerto Rico", "Mayaguez, Puerto Rico, USA",
  "B.Sc. Mathematics and Statistics", "1996-2001", "Univ. San Antonio Abad", "Cusco, Perú"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

-   **Rivera, R., Rosenbaum, J., and Quispe, W. (May 2020)**

Excess mortality in the United States during the first three months of the COVID- 19 pandemic, *Epidemiology and Infection, 148, E264. Cambridge University Press*.

-   **Quispe, W. (Dic 2019)**

Temporal outlier detection using dynamic Bayesian networks and probabilistic assciacion rules, *Phd Dissertation, University of Puerto Rico at Mayaguez*.

# Presentations

-   **E. Acuña, W. Quispe, R. Megret, and J. Agosto. (May 2019)**

Clustering using Functional Data Analysis for Honeybees Daily Activity Data, *Latin American Conference on Statistical Computing (ICORS-LACSC) , Guayaquil, Ecuador*.

# Software Skills

```{r}
tribble(
 ~Desc,
 "Python, R, Matlab, SQL, Apache-Spark, Latex"
) %>% 
  brief_entries(
    Desc
  )
```

# Interests

```{r}
tribble(
 ~Desc,
 "Data Science, Artificial Intelligence, Machine Learning, Anomaly Detection, Bayesian Statisics, Model Risk Management"
) %>% 
  brief_entries(
    Desc
  )
```
